% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[11pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\usepackage{verbatim}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Md Mustafizur Rahman }\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header
\name{Md Mustafizur Rahman\\[12pt]}% the \\[12pt] adds a blank line after name

\address{\\ School of Information \\
  University of Texas at Austin \\  1616 Guadalupe Ste 5.202 \\ Austin, TX 78701 \\ {\bf Email}: \href{mailto:nahid@utexas.edu}{nahid@utexas.edu}
  \\ {\bf Website}: \url{https://www.ischool.utexas.edu/~nahid/}
  \\ {\bf Google Scholar}: 
  \url{https://scholar.google.com/citations?user=-Lae4twAAAAJ&hl} 
  }
\begin{comment}


  \\ LinkedIn: \urlstyle{same}\url{https://www.linkedin.com/in/nahidcse05} 
  \\ Github: \urlstyle{same}\url{https://github.com/mdmustafizurrahman}
  \\ Number of Scholarly Publications: 24
  \\ Citation Count: 120
  \\ Country of Citizenship: Bangladesh
  \\ First date of entry to USA: August 16, 2014
  \\ Current Visa Status: F-1 
  \\ Current I-20 expire date: May 31, 2021
 \end{comment}

  

\address{{\bf } \\ }


\begin{resume}
\section{RESEARCH INTERESTS}
Information Retrieval, Machine Learning


\section{EDUCATION}
{\sl Ph.D. in  Information Studies (in progress)}\\
University of Texas at Austin, TX 78712 \hspace{1.45in} GPA 3.86 \hfill  August 2016 - present\\
Area - Information Retrieval\\
Adviser - Dr. Matthew Lease


{\sl Master of Computer Science}\\
University of Virginia, VA 22903 \hspace{2.00in} GPA 3.72\hfill  May 2016\\
Area - Text Mining\\
Thesis - Hidden Topic Sentiment Model\\
Adviser - Dr. Hongning Wang

{\sl Master of Science in Computer Science \& Engineering} \\
Bangladesh University of Engineering \& Technology, Dhaka \hspace{0.2in}  GPA 3.83 \hfill August 2013 \\
Area - Machine Learning\\
Thesis - Forecasting Time Series - An Ensemble based approach\\
Adviser - Dr. Md. Monirul Islam

{\sl Bachelor of Science in Computer Science \& Engineering} \\
Bangladesh University of Engineering \& Technology, Dhaka \hspace{0.2in}  GPA 3.95 \hfill February 2011 \\
Area - Sensor Network\\
Thesis - Detecting Cuts in Wireless Sensor Network \\
Adviser - Dr. Masud Hasan and Dr. Mahmuda Naznin

\vspace{0.05in}
\section{RESEARCH EXPERIENCE}
%\vspace{8pt}

{\sl Graduate Research Assistant} \hfill        September 2016  - present \\
School of Information\\
University of Texas at Austin\\
Adviser - Dr. Matthew Lease \\
Topic - Information Retrieval

\begin{itemize} \itemsep -2pt 
\item{Efficient Test Collection Construction via Active Learning.} {(under revision)} 
\item{Constructing Test Collections using Multi-armed Bandits and Active Learning.} {(under review)}
\item{Co-Training for Neural Network Modeling under Low Supervision} {- Developed a Co-Training approach which bootstraps the neural model using one or more simpler learning models and a pool of unlabeled data.}
\item{Answer Selection in Non-factoid Question Answering using Deep Learning}
          {- Developed a Convolutional Neural Network (CNN) based approach for non-factoid question answering.}
\end{itemize}


{\sl PhD Research Intern} \hfill    May 2018 - August 2018\\
Samsung Research America\\
Mountain View, CA \\
Adviser - Hongxia Jin \\
Topic - Open Domain Question Answering using Wikipedia
\begin{itemize} \itemsep -2pt
    \item Developed a context related question answering system for Samsung {\it Bixby} using a reading comprehension model and a learning to rank model
\end{itemize}
}


{\sl Applied Machine Learning Intern} \hfill    June 2017 - August 2017\\
Los Alamos National Laboratory\\
Los Alamos, NM \\
Adviser - Sunil Thulasidasan \\
Topic - Semi-supervised Deep Learning for Understanding Cancer Pathology Reports
\begin{itemize} \itemsep -2pt % reduce space between items

    \item Developed a semi-supervised graph-based deep learning model that leverages both labeled and unlabeled data points.
    \item Extracted clinical information from cancer pathology reports for automatic cancer type and site detection.
    \item Pre-processed cancer pathology reports by performing the sentence boundary disambiguation using a Maximum Entropy model and a Bi-directional LSTM deep model.

\end{itemize}

{\sl Graduate Research Assistant} \hfill        June 2015 - August 2015 \\
Department of Computer Science\\
University of Virginia\\
Adviser - Dr. Hongning Wang \\
Topic - Computational User Behavior Modelling

   \begin{itemize} \itemsep -2pt % reduce space between items
   \item Implemented several probabilistic topic models including 2-topic mixture model, probabilistic latent semantic analysis (pLSA), hidden topic markov model (HTMM).
   \item Developed a Hidden Markov Model based generative model to capture users' sentiments along with topics.
\end{itemize}

{\sl  Graduate Researcher}  \hfill  April 2012 - August 2013 \\
Department of Computer Science \& Engineering\\
Bangladesh University of Engineering \& Technology\\
Adviser - Dr. Md. Monirul Islam \\
Topic - Ensemble based approach for time series forecasting
 \begin{itemize} \itemsep -2pt
  \item  Developed a novel layered ensemble architecture for time series forecasting.
\end{itemize} \vspace{-6pt}

\vspace{0.1in}

\section{SELECTED PUBLICATIONS}
\vspace{-2pt}

{\large \bf Work in progress} 
\vspace{2pt}
\begin{enumerate} \itemsep -2pt
\item \textbf{Md Mustafizur Rahman}, Mucahid Kutlu, Tamer Elsayed, and Matthew Lease, ``Efficient Test Collection Construction via Active Learning'', under revision in the {\it Journal of the Association for Information Science and Technology (JASIS\&T)} 

\item \textbf{Md Mustafizur Rahman}, Mucahid Kutlu, and Matthew Lease,``Constructing Test Collections using Multi-armed Bandits and Active Learning'', under review in {\it The Web Conference (WWW 2019)}  

\end{enumerate}


{\large \bf Journal}  ({\sl \textbf{Work done at UT Austin, Texas}})
\begin{enumerate} \itemsep -2pt

 \item Kezban Dilek Onal, Ye Zhang, Ismail Sengor Altingovde, \textbf{Md Mustafizur Rahman}, Pinar Karagoz, Alex Braylan, Brandon Dang, Heng-Lu Chang, Henna Kim, Quinten McNamara, Aaron Angert, Edward Banner, Vivek Khetan, Tyler McDonnell, An Thanh Nguyen, Dan Xu, Byron C. Wallace, Maarten de Rijke, and Matthew Lease. ``Neural Information Retrieval: At the End of the Early Years''. {\it Information Retrieval Journal}, June 2018. Springer.\\ %[Online]. Available: \urlstyle{same}\url{https://link.springer.com/article/10.1007\%2Fs10791-017-9321-y}
\end{enumerate}


{\large \bf Journal} ({\sl \textbf{Work done at BUET, Bangladesh}})
\begin{enumerate} \itemsep -2pt
 \item {\bf Md Mustafizur Rahman}, Md. Monirul Islam, Kaziyuki Murase and Xin Yao. ``Layered Ensemble Architecture for Time Series Forecasting''. {\it IEEE transaction on Systems, Man & Cybernetics}, 46(1): 270 - 283, January 2016. (\textbf{Impact Factor: 7.38}) %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/TCYB.2015.2401038}
 
 \item Mohammad Raihanul Islam, {\bf Md. Mustafizur Rahman}, Asif Salekin, and Ahmed Shayer Andalib, ``A Novel Approach for Generating Clustered Based Ensemble of Classifiers,'' {\it International Journal of Machine Learning and Computing}, vol. 3, no. 1, pp. 137-141, 2013. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.7763/IJMLC.2013.V3.288}

 \item {\bf Md Mustafizur Rahman}, S. M. Ferdous, Syed Ishtiaque Ahmed, and Anika Anwar, ``Speech Development of Autistic Children by Interactive Computer Games,'' {\it Interactive Technology and Smart Education (ITSE)}, Emerald, vol. 8, no. 4, pp. 208 - 223, 2011. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1108/17415651111189450}

\end{enumerate}

{\large \bf Conference Proceedings}\\
\vspace{2pt}
\noindent\textbf{\textit{Long Paper}} ({\sl \textbf{Work done at University of Virginia, VA}})
\begin{enumerate} \itemsep -2pt

    
    \item {\bf Md Mustafizur Rahman} and Hongning Wang. ``Hidden Topic Sentiment Model''. In {\it Proceedings of the 25th International World Wide Web conference (WWW 2016)}, ACM, Montréal, Québec, Canada, pp. 155 - 165, April 2016. (\textbf{Acceptance Rate: 16\%}) %[Online]. Available: \urlstyle{same}\url{http://dl.acm.org/citation.cfm?id=2883072} 
\end{enumerate}
\textbf{\textit{Long Papers}} ({\sl \textbf{Work done at BUET, Bangladesh}})
  
\begin{enumerate}

    \item S. M. Ferdous, {\bf Md Mustafizur Rahman}, and Mahmuda Naznin. ``Finding Network Connectivity Failure in a Wireless Sensor Network''. In {\it Proceedings of the IFIP/IEEE Wireless Days}, IEEE, France, pp. 299 - 304, March 2016. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/WD.2016.7461522}
    
    \item {\bf Md Mustafizur Rahman}, S. K. K. Santu, Md. Monirul Islam, and Kazuyuki Murase. ``Forecasting Time Series - A Layered Ensemble Architecture''. In {\it Proceedings of the International Joint Conference on Neural Networks (IJCNN 2014)}, IEEE, Beijing, China, pp. 210 - 217, July 2014. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/IJCNN.2014.6889682}
    
    \item S. K. K. Santu, {\bf Md Mustafizur Rahman}, Md. Monirul Islam, and Kazuyuki Murase. ``Towards better generalization in Pittsburgh Learning Classifier Systems''. In {\it Proceedings of the IEEE World Congress on Computational Intelligence (CEC 2014)}, IEEE, Beijing, China, pp. 1666 - 1673, July 2014. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/CEC.2014.6900388}
    
    \item Nashid Shahriar, Mahfuza Sharmin, Reaz Ahmed, {\bf Md Mustafizur
    Rahman}, Raouf  Boutaba, and  Bertrand  Mathieu. ``Diurnal Availability for Peer-to-Peer
    Systems''. In {\it Proceedings of the IEEE Consumer Communications and Networking Conference (CCNC)}, Las Vegas, NV, USA, pp. 619 - 623, January 2012. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/CCNC.2012.6181140}

    \item S.  M.  Ferdous,  Anindya  Das,  M.  Sohel  Rahman, and  {\bf Md
    Mustafizur  Rahman}. ``An Ant Colony Optimization approach to solve the
    Minimum  String Cover Problem". In {\it Proceedings of the International Conference on Informatics, Electronics & Vision (ICIEV)}, Dhaka, pp. 741-746, May 2012. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICIEV.2012.6317422}
    
    \item  Azad Abdus Salam, Md. Kamrul Hasan, M.Arif Imtiazur Rahman, {\bf Md Mustafizur Rahman}, and Nashid Shahriar. ``Changing trends of climate in Bangladesh and a noble procedure of distribution of rainfall by clustering''. In {\it Proceeding of the International Conference on Statistical Data Mining for Bioinformatics Health Agriculture and Environment}, Rajshahi, Bangladesh, pp. 405 - 411, December 2012. ISBN: 978-984-33-5876-9.
    
    
    \item  Arshia Zernab Hassan, Bushra Tasnim Zahed, Fatema Tuz Zohora, Johra Muhammad Moosa, Tasmiha Salam, and {\bf Md Mustafizur Rahman}. ``Developing the Concept of Money by Interactive Computer Games for Autistic Children''. In {\it Proceedings of the IEEE Symposium on Multimedia}, IEEE Computer Society Press, California, USA, pp. 559 - 564, December 2011. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ISM.2011.99}
    
    \item {\bf Md Mustafizur Rahman}, S. M. Ferdous, and Syed Ishtiaque Ahmed. ``Increasing intelligibility in the speech of the autistic children by an interactive computer game''. In {\it Proceedings of the IEEE Symposium on Multimedia}, IEEE Computer Society Press, Taiwan, China, pp. 383-387, December 2010. %[Online]. Available: \urlstyle{same}\url{http://doi.ieeecomputersociety.org/10.1109/ISM.2010.64}
    
    
\end{enumerate}    


\textbf{\textit{Short Papers}} ({\sl \textbf{Work done at BUET, Bangladesh}})
\begin{enumerate} \itemsep -2pt    

    \item  Sajedul Karim Talukder, M. I. I. Sakib, and {\bf Md Mustafizur Rahman}. ``Model for E-Government in Bangladesh: A Unique ID Based Approach''. In {\it Proceedings of the International Conference on Informatics, Electronics & Vision (ICIEV)}, Dhaka, Bangladesh, May 2014. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICIEV.2014.7136000}
    
    \item Sajedul Karim Talukder, M. I. I. Sakib, and {\bf Md Mustafizur Rahman}. ``Digital Land Management System: A new initiative for Bangladesh''. In {\it Proceedings of the International Conference on Electrical Engineering and Information & Communication Technology (ICEEICT)}, Dhaka, Bangladesh, April 2014. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICEEICT.2014.6919031}
    
    \item  K.M.A. Solaiman, {\bf Md Mustafizur Rahman}, and Nashid Shahriar.
    ``AVRA Bangladesh collection, analysis \& visualization of road accident
    data in Bangladesh''. In {\it Proceedings of the International Conference on Informatics, Electronics \& Vision (ICIEV)}, IEEE, Dhaka, Bangladesh, May 2013. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICIEV.2013.6572632}
    
    \item  Asif Salekin, {\bf Md Mustafizur Rahman} and Shihab Hasan Chowdhury.
    ``Pattern matching in time series using combination of neural  network and
    rule based approach''. In {\it Proceedings of the 7th International
    Conference  on  Electrical  \& Computer Engineering (ICECE 2012)},  Dhaka,
    Bangladesh, pp. 478 - 481, December 2012. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICECE.2012.6471591}

    \item  Asif Salekin, {\bf Md Mustafizur Rahman}, and Raihanul Islam.
    ``Composite Pattern Matching in Time Series''. In {\it Proceedings of the
    15th International Conference on Computer \& Information Technology (ICCIT 2012)},
    Chittagong, Bangladesh, December 2012. %[Online].\\Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICCITechn.2012.6509784}

    
\end{enumerate}   


\textbf{\textit{Poster Presentation}} ({\sl \textbf{Work done at UT Austin, TX}})
\begin{enumerate} \itemsep -2pt    

    \item Malay Bhattacharyya, Yoshihiko Suhara, \textbf{Md Mustafizur Rahman}, and Markus Krause. ``Possible Confounds in Word-based Semantic Similarity Test Data''. In {\it Proceedings of the 20th ACM Conference on Computer-Supported Cooperative Work and Social Computing (CSCW 2017)}, ACM, Portland, OR, USA, pp. 147 - 150, February 2017. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1145/3022198.3026357} 
\end{enumerate}
\textbf{\textit{Poster Presentations}} ({\sl \textbf{Work done at BUET, Bangladesh}})   

\begin{enumerate}


    \item Mohammad Raihanul Islam, {\bf Md Mustafizur Rahman}, Asif Salekin, Shihab Hasan Chowdhury, and Samiul Alam Anik. ``A
    Novel Clustering-Based Ensemble Classification Model for Block Learning''.
    In {\it Proceedings of the 2nd International Conference on Pattern
    Recognition Applications and Methods (ICPRAM 2013)}, Barcelona, Spain, pp. 285 - 288, February 2013.
    
    
    \item Mirfat Akter Sharmin, Md. Mizanur Rahman, Syed Ishtiaque Ahmed, {\bf Md Mustafizur Rahman}, and S. M. Ferdous. ``Teaching intelligible speech to the Autistic children by interactive computer games''. In {\it Proceedings of the ACM Symposium on Applied Computing}, ACM Press, Taiwan, China, pp. 1208 - 1209, March 2011. %[Online] Available: \urlstyle{same}\url{http://dx.doi.org/10.1145/1982185.1982450}
    
    \item Anika Anwar, {\bf Md Mustafizur Rahman}, S. M. Ferdous, Samiul Alam Anik, and Syed Ishtiaque Ahmed. ``A Computer Game based Approach for Increasing Fluency in the Speech of the Autistic Children''. In {\it Proceedings of the IEEE International Conference on Advanced Learning Technologies}, IEEE Computer Society Press, Athens, Georgia, USA, pp. 17 - 18, July 2011. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1109/ICALT.2011.13}
\end{enumerate}   


{\large \bf Book Chapter} ({\sl \textbf{Work done at BUET, Bangladesh}})
\vspace{2pt}
\begin{enumerate} \itemsep -2pt
\item Abdus Salam Azad, Md. Kamrul Hasan, M. Arif Imtiazur Rahman, {\bf Md. Mustafizur Rahman}, and Nashid Shahria. ``Exploring the Behavior and Changing Trends of Rainfall and Temperature Using Statistical Computing Techniques''. {\it Computational Intelligence Techniques in Earth and Environmental Sciences}, Springer, pp. 53 - 78, January 2014. %[Online]. Available: \urlstyle{same}\url{http://dx.doi.org/10.1007/978-94-017-8642-3_3}
\end{enumerate}


\begin{comment} \itemsep -2pt 

 \item  Arshia Zernab Hassan, Bushra Tasnim Zahed, Fatema Tuz Zohora, Johra Muhammad Moosa, Tasmiha Salam, {\bf Md Mustafizur Rahman}, Hasan Shahid Ferdous, and Syed Ishtiaque Ahmed. ``Socializing Autistic Children with Interactive Computer Games''. In Proceedings of the IEEE Newsletter on Learning Technologies, Vol. 13, Issue 4, pp. 62 - 65, October 2011.
    
    \item  Ali S. Sabbir, Khosru Md. Salim, Md. Raihan B. Rafique, M Omar Rahman, {\bf Md Mustafizur Rahman}, Md. Hasanuzzaman Bhuiyan, Hasan S. Ferdous, and Syed I. Ahmed. ``Birth Record Communicator: A Pathway to Automated Health Data Acquisition System''. Workshop on Interactive Systems in Healthcare at Annual Symposium of the American Medical Informatics Association (AMIA), Washington, DC, USA, October 2011. 
    [Online]. Available: \urlstyle{same}\url{https://wish2011.wordpress.com/accepted-papers/}

    
   \end{comment}




\begin{comment}
\section{PROGRAM COMMITTEE MEMBER}
{\sl Conference}
%\vspace{2pt}
\begin{itemize} \itemsep -2pt
\item The Fourth AAAI Conference on Human Computation and Crowdsourcing (HCOMP 2016), October 30 - November 3, 2016, Austin, TX, USA
 \end{itemize}
 \end{comment}

\section{ORGANIZING COMMITTEE MEMBER}
{\sl Conference}
%\vspace{2pt}
\begin{itemize} \itemsep -2pt
\item Workshop on Computational Intelligence (WCI 2012), Dhaka, Bangladesh
\item Workshop on Algorithm and Computation (WALCOM 2012), Dhaka, Bangladesh
\item Workshop on Graph Drawing and Graph Algorithm (GDGA 2013), Dhaka, Bangladesh
\item Workshop on Women Empowerment through ICT: Higher
Studies, Research, and Career (WE-ICT 2014), Dhaka, Bangladesh

 \end{itemize} 


\section{REVIEWER}
{\sl Conference}
%\vspace{2pt}
\begin{itemize} \itemsep -2pt
\item The Fourth AAAI Conference on Human Computation and Crowdsourcing (HCOMP 2016)
 \end{itemize}

\begin{comment}
\section{SELECTED PROJECTS}
{\sl Graduate Research Projects}
\vspace{2pt}
\begin{itemize} \itemsep -2pt
\item \textbf{Semi-Supervised Deep Learning for Deep-NLP: Clinical Information Extraction from Cancer Pathology Reports} \\
- Developed a semi-supervised graph-based regularization deep learning model that leverages both labeled and unlabeled data points \\
- Extracted clinical information from cancer pathology reports for automatic cancer type and site detection \\ 
- Pre-processed cancer pathology reports by performing sentence boundary disambiguation using Maximum Entropy and Bi-directional LSTM deep model 

\item \textbf{Literature Review on Neural Information Retrieval} \\
- Surveyed the current landscape of Neural Information Retrieval (IR) research paying special attention to the use of learned representations of queries and documents (i.e., neural embedding)\\
- Accepted as a journal paper in Information Retrieval Journal, Springer

\item \textbf{Answer Selection in Non-Factoid Question Answering using Deep Learning}\\
- Applied Convolutional Neural Network (CNN) on Non-factoid Question Answering\\
- Leveraged word embedding for semantic representation\\
- Performed answer selection using similarity measure between the semantic vector of questions and answers
 
\item \textbf{Open Source Machine Learning Package} \\ 
- Developed several supervised, semi-supervised, unsupervised machine learning algorithms for working with text data analysis\\ 
- Designed using full-scale object-oriented fashion and support extension for several base algorithms
%- Development is still ongoing and open to anyone for collaboration on Github \urlstyle{same}\url{https://github.com/Linda-sunshine/IR_Base}

\item \textbf{Topic Modeling for Unstructured Text Document} \\
- Developed a Hidden Markov Model based topic model which captures the transition of users' sentiment on a sentence by sentence basis \\ 
- Crawled dataset of customer reviews from Amazon.com and NewEgg.com and applied our model\\
- Accepted as a full research paper in the 25th International World Wide Web conference (WWW 2016), Canada, 2016

\item \textbf{Sentiment Analysis on IMDB Movie Reviews} \\
- Developed a multi-class sentiment classification algorithm for labeling the sentiment label of IMDB movie review \\
%- Language and framework used in this project are Python, Google Word2Vec, JSON and Sci-kit\\ 
%- Successfully participated in Kaggle Competition - \textit{Bag of Words Meets Bags of Popcorn} \urlstyle{same}\url{https://www.kaggle.com/c/word2vec-nlp-tutorial/leaderboard}

\item \textbf{Personalized Job Matching} \\
- Developed multiple crawlers for crawling job-postings from Google, Facebook, Microsoft, and IBM \\ 
- Indexed 1GB of crawled data using Apache Lucene \\
- Designed a rank model based on indexed results and developed an interface to show the search results for a given search query

\end{itemize}


{\sl Undergraduate Software Projects}
\vspace{2pt}
\begin{itemize} \itemsep -2pt
 \item \textbf{Social Bookmarking  Website} - Developed a website for online bookmarking/ voting for other websites.  The website was developed in PHP  and MySQL server. CSS and HTML have been used for user interface
 \item \textbf{Automated  System  for  Buying  House} - Designed  the  use-case model, collaboration and class diagram, sequence diagram and input-output of a buying  house system using UML
 \item \textbf {Photo  Viewer} - Developed a simple  photo  viewing  software  using  JAVA  which has the ability  to  view  various formats
of picture ( i.e.: jpg, jpeg, tiff, bmp etc.)   
 \item \textbf{Data Link Layer Implementation} - Implemented the sliding window protocol of Data Link Layer (one of the OSI layers) using Java
 \item \textbf{Kernel of an Operating System} - Developed the kernel and the shell of an operating system as part of a larger operating system (OS) using educational OS named NACHOS. The kernel had an architecture similar to UNIX and was developed using C language
\end{itemize}
\vspace{2pt}
{\sl Undergraduate Hardware Projects}
\vspace{2pt}
\begin{itemize} \itemsep -2pt
 \item \textbf{4-bit  Digital  Computer} - Designed  and  developed  a  digital  computer  capable  of  executing  $28$
instructions from the  Intel  80x86 processor family.  Its  main  features  include a shared  bus, a microprogrammed control unit and separate data and instruction RAM
 \item \textbf{Modified Booth's Multiplier} - Designed and implemented a modified version of Booth’s
multiplier which was capable of multiplying ten bits multiplication in 2's complement form

\end{itemize}


\section{RELATED COURSEWORKS}
\vspace{8pt}
\begin{tabular}{l l}
     \textbf{Graduate}& \textbf{Undergraduate} \\
     Information Retrieval & Discrete Mathematics \\
     Text Mining & Algorithms \\
     Advanced Algorithms &  Artificial Intelligence\\
     High Dimensional Data Management & Mathematical Analysis for Computer Science\\
     Neural Networks & \\
     Data Science in Software Engineering & \\
     Theory of Computation & \\
\end{tabular}
\end{comment}

\section{TEACHING EXPERIENCE}
{\sl Graduate Teaching Assistant} \hfill        Fall 2014, Spring 2015, Fall 2015, Spring 2016\\
Department of Computer Science\\
University of Virginia\\
\begin{itemize} \itemsep -2pt % reduce space between items
   \item CS 4750 (Database Design): Spring 2016,  Course Instructor: Prof. Nada Basit
   \item CS 2102 (Discrete Mathematics) Spring 2016, Course Instructor: Prof. David Edwards
   \item CS 4501 (Information Retrieval): Fall 2015, Course Instructor: Prof. Hongning Wang 
   \item CS 3102 (Theory of Computation): Fall 2015, Course Instructor: Prof. Worthy Martin
   \item CS 3102 (Theory of Computation): Spring 2015, Course Instructor: Prof. Gabriel Robins
   \item CS 3102 (Theory of Computation): Fall 2014, Course Instructor: Prof. Worthy Martin
   \item CS 4810 (Computer Graphics): Fall 2014 Course Instructor: Prof. Jason Lawrence
\end{itemize}

{\sl Assistant Professor} \hfill    February 2014 - August 2014\\
Department of Computer Science \& Engineering\\
Bangladesh University of Engineering \& Technology \\
\begin{comment}
\begin{itemize} \itemsep -2pt % reduce space between items
   \item CSE 307 (Software Engineering \& Information System Design)
\end{itemize}
\end{comment}

{\sl Lecturer} \hfill    March 2011 - January 2014\\
Department of Computer Science \& Engineering\\
Bangladesh University of Engineering \& Technology \\
\begin{comment}
\begin{itemize} \itemsep -2pt % reduce space between items
   \item CSE 105 (Structured Programming Language)
   \item CSE 201 (Object Oriented Programming Language)
\end{itemize}
\end{comment}

\begin{comment}

{\sl Adjunct Faculty} \hfill August 2011 - July 2014\\
Department of Computer Science \& Engineering\\
Ahsanullah University of Science and Technology, Dhaka, Bangladesh\\


{\sl Adjunct Faculty} \hfill August 2011 - July 2014\\
Department of Computer Science \& Engineering\\
University of Liberal Arts Bangladesh, Dhaka, Bangladesh\\

{\sl Adjunct Faculty} \hfill February 2013 - July 2014\\
Department of Computer Science \& Engineering\\
East West University, Dhaka, Bangladesh\\

{\sl Adjunct Faculty} \hfill February 2012 - November 2012\\
Department of Computer Science \& Engineering\\
State University of Bangladesh, Dhaka, Bangladesh\\

\vspace{0.2in}
\section{SOFTWARE ENGINEER}
\vspace{8pt}
{\sl Quantitative Software Developer, Part-time} \hfill November 2010 - July 2014\\
Stochastic Logic Limited, Dhaka, Bangladesh\\
\end{comment}


\section{HONORS}
\begin{itemize} \itemsep -2pt
\begin{comment}
 \item Full tuition waiver and graduate assistantship, School of Information, University of Texas at Austin \hfill 2016--2021
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, Texas A \& M University (not availed) \hfill 2016--2021
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, the University of Texas at Dallas  (not availed)  \hfill 2016--2021
 
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, the University of Texas at Arlington  (not availed)  \hfill 2016--2012
 
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, the University of Texas at San Antonio (not availed) \hfill 2016--2021
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, University of Virginia \hfill 2014--2016
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, Stony Brook University, New York (not availed) \hfill 2014--2019
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, University of British Columbia, Canada (not availed) \hfill 2014--2019
 
 \item Full tuition waiver and a graduate assistantship, Department of Computer Science, University of Waterloo, Canada (not availed) \hfill 2014--2019

\end{comment}
 
 
 \item Full scholarship to attend a workshop on research frontier in Computing from School
of Computing (SoC), National University of Singapore (NUS), Singapore.  May 2012
  \item  Awarded with a scholarship from Institute of International Education, New York, USA sponsored
by AIG Foundation \hfill 2006--2011
\item  Deans list award for academic excellence from Bangladesh University of Engineering \& Technology\hfill
2006--2011
\item  University scholarship for academic excellence from Bangladesh University of Engineering \& Technology \hfill 2006--2011
\item Award of excellence from Nazrul Islam Hall, Bangladesh University of Engineering \& Technology \hfill 2011
\end{itemize}

\begin{comment}

\section{TECHNICAL SKILLS}
%\begin{itemize} \itemsep -2pt
\textbf{Programming language}: C, C++, Java, SQL, Python, Scala, \LaTeX, \TeX \\
\textbf{Scientific Computing}: Matlab, WEKA \\
\textbf{Open Source Packages}: Apache Lucene, Apache OpenNLP \\
\textbf{Big Data Tools}: Elasticsearch, Apache Spark, Spark-SQL, Hive\\
\textbf{Web Programming}: HTML, CSS, PHP, Jade, JavaScript, Node.js \\
\textbf{Database Management System}: Oracle, MySQL, MongoDB, JSON \\
\textbf{Data Mining/Machine Learning}: Naive Bayes, Logistic Regression, Linear Regression, Neural Networks, Support Vector Machine, K-Nearest Neighbour, K-means, Recommendation Systems, Expectation Maximization (EM), Hidden Markov Model, Natural Language Processing (NLP) \\
\textbf{Text mining}: Language Model, Probabilistic Latent Semantic Analysis (pLSA), Latent Dirichlet Allocation (LDA), Hidden Topic Markov Model (HTMM)\\
\textbf{Version Control}: Git \\
\textbf{Project Build Tools:} Apache Maven, SBT \\
\textbf{Operating Systems}: Microsoft Windows, Linux
\end{comment}



%\vspace{0.2in}
\begin{comment}
\section{COURSEWORK}
\textbf{Graduate}
\begin{itemize} \itemsep -2pt
\item Information Retrieval 
\item Text Mining
\item High Dimensional Data Management
\item Data Mining in Software Engineering
%\item Database System
\item Big Data in Health
\item Advanced Algorithm 
\item Meta-Heuristics 
%\item Software Engineering
\end{itemize}


\textbf{Undergraduate}
\begin{itemize} \itemsep -2pt
\item Operating Systems 
\item Artificial Intelligence + Practicum 
\item Functional Programming 
\item Computer Graphics + Practicum 
\end{itemize}
\end{comment}


\vspace{0.2in}


%\newpage
\section{REFERENCES}

\vspace{0.2in}
\begin{tabular}{ l l } 
Dr. Matthew Lease & Dr. Mucahid Kutlu\\
Associate Professor & Assistant Professor \\
School of Information & Department of Computer Engineering \\
University of Texas at Austin & TOBB Economy and Technology University \\
{E-mail: ml@utexas.edu } & {E-mail: m.kutlu@etu.edu.tr} \\
\urlstyle{same}\url{https://www.ischool.utexas.edu/~ml/} & \urlstyle{same}\url{https://www.etu.edu.tr/en/}\\
& \\
Sunil Thulasidasan & Dr. Hongning Wang\\
Scientist & Assistant Professor \\
Information Sciences Group & Department of Computer Science \\
Los Alamos National Laboratory &  University of Virginia \\

{E-mail: sunil@lanl.gov} & {E-mail: hw5x@virginia.edu} \\
\urlstyle{same}\url{http://public.lanl.gov/sunil/} & \urlstyle{same}\url{http://www.cs.virginia.edu/~hw5x/}\\
\end{tabular}
\end{resume}
\end{document}













